Introductory statistics with `intRo`

### 2016-06-15 jcgs-paper-2016/paper.Rmd
Width cutoff for tidy opts

\footnotesize
```{r ui, eval=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=25)}
## Source ui
mylist <- list()
old_heading <- ""
for (i in seq_along(modules)) {
    my.module <- strsplit(modules[i], "/")[[1]]
    if (my.module[1] != old_heading) {
        mylist[[length(mylist) + 1]] <- Hmisc::capitalize(my.module[1])
        old_heading <- my.module[1]
    }
    mylist[[length(mylist) + 1]] <- get(paste(my.module[2], "ui", sep = "_"))
}

@@

\footnotesize
```{r server, eval=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=25)}
shinyServer(function(input, output, session) {
    types <- c("helper.R", "observe.R", "reactive.R", "output.R")

>>>>

\footnotesize
```{r ui, eval=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=50)}
## Source ui
mylist <- list()
old_heading <- ""
for (i in seq_along(modules)) {
    my.module <- strsplit(modules[i], "/")[[1]]
    if (my.module[1] != old_heading) {
        mylist[[length(mylist) + 1]] <- Hmisc::capitalize(my.module[1])
        old_heading <- my.module[1]
    }
    mylist[[length(mylist) + 1]] <- get(paste(my.module[2], "ui", sep = "_"))
}

@@

\footnotesize
```{r server, eval=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=50)}
shinyServer(function(input, output, session) {
    types <- c("helper.R", "observe.R", "reactive.R", "output.R")
